mouse level quality plots

### 2019-11-12 doc/MouseLevelPlots.Rmd
updated the mouse level count by quality plots. started list of mice to exclude

---
title: "mouse level quality plots"
author: "April Peterson"
date: "August 29, 2019"
output: html_document
---

@@

#load main data file
load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!

@@

knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

These MLH1 data still have quality 5 cells observations. I might want to redo it without those observations.

@@

#mice that don't have female data will break the chain-loop
#MOLF female, HMI, CZECH female, CAROLI female, Tom male

#instead of adding fake data, remove the categories from list

#filler_data_MOLF.f = c("BatchX", "1jan19_fake_MOLF_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_MOLF_f1_sp1_rev.tif",
#                       "fake_MOLF_f1", "MOLF female", "MOLF","female","Musc", "20","")
#filler_data_HMI.f = c("BatchX", "1jan19_fake_HMI_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_HMI_f1_sp1_rev.tif",
#                       "fake_HMI_f1", "HMI female", "HMI","female","Cast", "20","")
#filler_data_CZECH.f = c("BatchX", "1jan19_fake_CZECH_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_CZECH_f1_sp1_rev.tif",
#                       "fake_CZECH_f1", "CZECH female", "CZECH","female","Musc", "20","")
#filler_data_CAROLI.f = c("BatchX", "1jan19_fake_CAROLI_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_CAROLI_f1_sp1_rev.tif",
#                       "fake_CAROLI_f1", "CAROLI female", "CAROLI","female","Caroli", "20","")
#MLH1_data_table <- rbind(MLH1_data, filler_data_MOLF.f,filler_data_HMI.f,filler_data_CZECH.f,filler_data_CAROLI.f)#error from dataset thing

pass_mice <- c("28sep18_CZECH_m3","26oct18_MOLF_m1","22jun15_G_m2")

#this loop makes a quant_status col for a list of mice
for(i in 1:length(MLH1_data$mouse)){
  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
}

df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#this is where you remove the non-data data!
df_list <- df_list[ -c(7,12,14,18,20,21,22,24,26,28,30) ]

#7 PERC, 12 MOLF female, 
#

@@

MLH1_data$quant_status <- as.factor(MLH1_data$quant_status)

@@

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ 
    geom_jitter(aes(y= adj_nMLH1.foci, x= quality)) + 
    geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5, xmin=-100, xmax=100, ymin=-100, ymax=100)+
    facet_wrap(~ mouse, drop = TRUE) + 
    geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +scale_fill_manual(values=c(NA, "red"), breaks=NULL) +    geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme(plot.background = element_rect(fill = "green")) #theme for indiviual mice, 
  #make an empty ggplot? for missing data

>>>>

---
title: "mouse level quality plots"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

@@

#load main data file
load(file="data/MLH1/MLH1_data_setup_11.12.19.RData")#added batch17
#load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!

@@

knitr::opts_chunk$set(echo = TRUE)

#remove other!
MLH1_data <- MLH1_data[MLH1_data$strain != "other",]

MLH1_data <- droplevels(MLH1_data)
```

@@

Yellow colored boxes are mice that will be exclude from the final (HQ) dataset for low quality cells (5). Consider re-runing this with the final data frame to see how the strain and mouse means change.

@@

@@

exclude_mice <- c("10mar15_WSB_m2", "8oct14_WSB_f1", "8oct14_WSB_f3", "18nov17_WSB_f5",
                  "8jun15_G_f3", "8jun15_G_f4",
                  "4jan17_LEW_f2",
                  "8oct14_PWD_f3", "1apr15_PWD_f2", "8oct14_PWD_f5",
                  "12sep16_MSM_f3",
                  "27oct18_MOLF_m3",
                  "26oct18_SKIVE_f1","26oct18_SKIVE_f2","26oct18_SKIVE_f3",
                  "27aug18_CZECH_m1","8jun18_CZECH_m1",
                  "3sep18_AST_m1",
                  "3jel18_TOM_m1","3sep18_TOM_m1",
                  "31jul17_HMI_m1",
                 "21aug17_SPI_f1", "30may18_SPIC_f1", "30oct17_SPIC_m1", "8jun18_SPIC_m2"
                  )

#based on this plot make a list of mice to exclude, and figure out code to outline in red
#mostly excluding based on number of 5quality cells

#mice.to.exclude <-

#WSB; "10mar15_WSB_m2", "8oct14_WSB_f1", "8oct14_WSB_f3", "18nov17_WSB_f5",
#G;  "8jun15_G_f3", "8jun15_G_f4"
#LEW; "4jan17_LEW_f2"
#PWD; "8oct14_PWD_f3", "1apr15_PWD_f2", "8oct14_PWD_f5"
#MSM; "12sep16_MSM_f3",#"14jul17_MSM_f1"
#MOLF; "27oct18_MOLF_m3"
#SKIVE; "26oct18_SKIVE_f1","26oct18_SKIVE_f2","26oct18_SKIVE_f3"
#CZECH; "27aug18_CZECH_m1","8jun18_CZECH_m1"
#AST: "3sep18_AST_m1"
#TOM; "3jel18_TOM_m1","3sep18_TOM_m1"
#HMI; "31jul17_HMI_m1"
#SPIC; "21aug17_SPI_f1", "30may18_SPIC_f1", #"30oct17_SPIC_m1", "8jun18_SPIC_m2",

#these plots are filled in yellow, but a different alpha/transparency is being applied - I don't know why

#this loop makes a quant_status col for a list of mice (THERE'S AN ARGUMENT FOR Drawing a box around the mouse blocks )
#switch this loop to ex
for(i in 1:length(MLH1_data$mouse)){
  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], exclude_mice), "exclude", NA)
}

#CZECH is not in this list!!!

df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#this is where you remove the non-data data!
df_list <- df_list[ -c(24, 29) ]

#12 MOLF female, 18 CZECH female?, 24 HMI female, 29 CAROLI female? 31 other
#

@@

#MLH1_data$quant_status <- as.factor(MLH1_data$quant_status)

@@

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ 
    geom_jitter(aes(y= adj_nMLH1.foci, x= quality)) + xlim(c(0.5,5.5))+

    #put a box over strain plots based on the col, 'quant_status'
      geom_rect(data = df_list[[h]], aes(fill= quant_status), alpha= 0.045, xmin=-100, xmax=100, ymin=-100, ymax=100)+

      scale_fill_manual(values=c("yellow"), breaks=NULL) +

    facet_wrap(~ mouse, drop = TRUE) + 
    geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +

      geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme(plot.background = element_rect(fill = "green")) #theme for indiviual mice, 
  #make an empty ggplot? for missing data
